\documentclass{llncs}
\usepackage{amsmath,amsfonts}

\begin{document}

\title{Private Location Verification}
\author{Vadym Fedyukovych}
\institute{Platin.io}
\maketitle

\abstract{
We present location verification protocol and implementation that allows for location privacy.
With a Schnorr-like protocol, we verify that location committed is close enough to another known location.
Protocol was implemented with {Crypto++} library.
}

\section{Introduction}

Need for location privacy.
Known results and state of the art.
SNARK-based and 'older' interactive proofs-based solutions.

\subsection{Our contribution}

\section{Protocol}
\subsection{Definitions}

Commitment, interactive proof system, witness indistinguishability and zero knowledge,
'algebraic' interactive proofs,
proving relations about integers,
groups of hidden order,
Rabin-Shallit algorithm,
extending Schnorr protocol into higher degrees of challenge.
Proofs and arguments, completeness and soundness, of knowledge, zero knowledge and witness indistinguishability.
Hardness of factoring and finding group order, StrongRSA.

\subsection{Notations}

Airdrop location $(x_l, y_l)$ available in clear, node location $(x_n, y_n)$ hidden (committed),
acceptable maximum distance $d$ from node to airdrop,
setup: group description and parameters, group elements for making commitments,
initial message, challenge and responces of a Schnorr-like protocol.

\subsection{Interactive proof}

Interactive argument system about integers is designed
with a group of a hidden order~\cite{},
that is, order of the group is not available to the Prover.
Inequality (not far from) statement is converted into equality
with 4-squares Lagrange theorem (Lipmaa).
Schnorr proof was extended into a proof systems for polynomial relations
with polynomials of higher degree in challenge
for a number of applications~\cite{F363,CF12}.
A comparable proof system for integers was introduced at~\cite{F10}.

\subsection{Proof setup}

Proof system for relations about integers is well described at Idemix documentation~\cite{Indemix}

Multiplicative group of residue classes, RSA-like modulus.

\begin{figure}[!htb]
\begin{tabular}{|p{\linewidth}|}
\hline

Common input of Prover and Verifier is
  commitment $s_U$ to node location~\eqref{cmt-up},
  airdrop location $(x_l, y_l)$,
  threshold $d^2$,
  and parameres $(g, g_x, g_y, g_r, h_j)$:
\begin{gather}
\label{cmt-up}
  s_U = g_x^{x_n} g_y^{y_n} g^{r}
\end{gather}
Private input of Prover is
  node location $(x_n, y_n)$ and location commitment randomness~$r$,
  four numbers~$\{a_j\}$ calculated with Rabin-Shallit algorithm according to~\eqref{eq-distn}.
Statement being proved is
\begin{gather}
\label{eq-distn}
  d^2 - ((x_n - x_l)^2 + (y_n - y_l)^2) = \sum_{j=1}^4 a_j^2
\end{gather}
Protocol runs as follows:
\begin{enumerate}
\item
  Prover picks random $\alpha_j, \eta, \gamma, \beta_x, \beta_y, \beta_r, \rho_0, \rho_1$,
  computes $f_0, f_1$, and sends initial commitments $b_0, b_1, t_a, t_n$:
\begin{gather}
  f_0 = -(\beta_x^2 + \beta_y^2) - \sum_{j=1}^4 \alpha_j^2,   \;
  f_1 = -2( (x_n - x_l) \beta_x  + (y_n - y_l) \beta_y) -2 \sum_{j=1}^4 a_j \alpha_j   \\
%
  t_n = g_x^{\beta_x} g_y^{\beta_y} g^{\beta_r} ,   \;
  s_a = g^{\gamma} \prod_{j=1}^4 h_j^{a_j},   \;
  t_a = g^{\eta} \prod_{j=1}^4 h_j^{\alpha_j}, \;
  b_0 = g^{f_0} g_r^{\rho_0},  \;
  b_1 = g^{f_1} g_r^{\rho_1}
\end{gather}
%
\item
  Verifier chooses and sends his challenge $c$
\item
  Prover computes and sends responses
\begin{gather}
  X_n = c x_n + \beta_x,  \;
  Y_n = c y_n + \beta_y,  \;
  R = c r + \beta_r   \\
  A_j = c a_j + \alpha_j, \;
  R_a = c \gamma + \eta,   \;
  R_d = c \rho_1 + \rho_0
\end{gather}
%
\item
  Verifier accepts if
\begin{gather}
\label{verf-linear}
  g_x^{X_n} g_y^{Y_n} g^{R} s_U^{-c} = t_n, \quad
  g^{R_a} (\prod_{j=1}^4 h_j^{A_j}) s_a^{-c} = t_a \\
\label{verf-distn}
  g^{c^2 d^2 - ((X_n - c x_l)^2 + (Y_n - c y_l)^2) - (A_1^2 + A_2^2 + A_3^2 + A_4^2)} g_r^{R_d} = b_1^{c} b_0
\end{gather}
\end{enumerate}
\\
\hline
\end{tabular}
\caption{Private location verification protocol}
\label{fig}
\end{figure}

\subsection{Security properties}

Completeness and Soundness.
We reduce

\section{Implementation}

We have this protocol implemented on top of {Crypto++} library~\footnote{\url{https://cryptopp.com/}}
serving as a bignumbers backend.

Producing four-squares witness~\cite{PollackTrevino} is a work in progress, and is not a part of the protocol reported.
To facilitate larger proof-of-concept application, a temporary approximate solution was introduced producing four squares.

\section{Discussion and Conclusion}

\bibliographystyle{splncs}
\bibliography{private_location_verification}

%\appendix
\end{document}
